Current and future constraints on primordial magnetic fields

### 2016-10-21 pmf.tex
a

\newcommand{\sqdeg}{deg$^2$ }
\newcommand{\omb}{\ensuremath{\Omega_b h^2}}
\newcommand{\omc}{\ensuremath{\Omega_c h^2}}
\newcommand{\clpp}{\ensuremath{C_{L}^{\phi\phi}}}
\newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm pmf}}}
\newcommand{\apmf}{\ensuremath{A_{\rm pmf}}}
\newcommand{\bpmf}{\ensuremath{B_{\rm 1\,Mpc}}}
\newcommand{\alens}{\ensuremath{A_{\rm lens}}}
\newcommand{\lcdm}{\ensuremath{\Lambda}CDM}
\newcommand{\nrun}{\ensuremath{n_{\rm run}}}
\newcommand{\neff}{\ensuremath{N_{\rm eff}}}
\newcommand{\mnu}{\ensuremath{\sum m|\nu}}
\newcommand{\fermilat}{\textit{Fermi}-LAT}

@@

>>>>

\newcommand{\sqdeg}{deg$^2$ }
\newcommand{\omb}{\ensuremath{\Omega_b h^2}}
\newcommand{\omc}{\ensuremath{\Omega_c h^2}}
\newcommand{\clpp}{\ensuremath{C_{L}^{\phi\phi}}}
\newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm pmf}}}
\newcommand{\apmf}{\ensuremath{A_{\rm pmf}}}
\newcommand{\bpmf}{\ensuremath{B_{\rm 1\,Mpc}}}
\newcommand{\alens}{\ensuremath{A_{\rm lens}}}
\newcommand{\lcdm}{\ensuremath{\Lambda}CDM}
\newcommand{\nrun}{\ensuremath{n_{\rm run}}}
\newcommand{\neff}{\ensuremath{N_{\rm eff}}}
\newcommand{\ho}{H\ensuremath{_0}}
\newcommand{\mnu}{\ensuremath{\sum m|\nu}}
\newcommand{\fermilat}{\textit{Fermi}-LAT}

@@

Given that CMB-S4 is still being designed, it is worthwhile to consider how the design decisions might influence the final PMF constraints. 
We look at four aspects of the experiment design: the telescope size or beam FWHM, the low-$\ell$ noise performance (1/f knee), and the choice of survey area, and how well the beam size and calibration must be known. 
Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs

Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefor always improve the PMF constraints. 
However, larger telescopes are also more expensive to build which means at fixed cost, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
We find the gains due to resolution at fixed mapping speed to be negligible: a beam size of FWHM=1$^\prime$ yields only a 1\% better limit than a FWHM of 10$^\prime$. 
This illustrates how important the large angular scales are to the PMF limits. 
We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin for a FWHM of 1$^\prime$. 
In this quasi-cost-neutral setup, there is a strong preference to go for more detectors over better angular resolution: the uncertainty was a factor of 2.5 times smaller in the coarse case over the FWHM=1$^\prime$ case. 
Raw sensitivity is more important than angular resolution to an experiment's ability to study PMFs.

However, adding more detectors does 
Of course,

If you don't require cost-

We assume the beam i

 the beam FWHM (i.e. telescope diameter),
